Notes: New gaugings in 3d from three-form

### 2023-06-15 Draft_3dH3.tex
Correction of the shift formula (6.13) (error comes from Log(T)=\psi on 13/06), and of the link to AdS3xS3 in (6.18).

Therefore, these deformations affect the Kaluza-Klein spectrum as follows: the conformal dimension of each physical field (\textit{c.f.} eq.~\eqref{eq:confdims3s3s1}) get shifted by replacing
\begin{equation} \label{eq:confdimshiftchi}
	2\pi n\longrightarrow e^{-2\psi} \left[ 2\pi n + \Big((q_{\rm L}+q_{\rm R})\,\frac{\chi_{1}}{\alpha}+(q_{\rm L}-q_{\rm R})\,\frac{\chi_{2}}{\alpha}+ (\ts{q}_{\rm L}+\ts{q}_{\rm R})\,\ts{\chi}_{1} + (\ts{q}_{\rm R}-\ts{q}_{\rm L})\,\ts{\chi}_{2}\Big) \right]\,,
\end{equation}
where the $q$ denote the charges under the different ${\rm U}(1)$.

@@

\begin{itemize}
	\item {\boldmath ${\cal N}=2$} The four-dimensional hypersurfaces
	\begin{equation} \label{eq:N2}
		\chi_{2} = \chi_{1} \pm\alpha\,(\ts{\chi}_{1}+\ts{\chi}_{2})% + 2\pi k 
		\quad {\rm or}\quad \chi_{2} = -\chi_{1} \pm\alpha\,(\ts{\chi}_{1}-\ts{\chi}_{2})% + 2\pi k \,, \qquad k \in \mathbb{Z}
		\,,
	\end{equation}
	give enhancements to ${\cal N}=(0,2)$ and ${\cal N}=(2,0)$, respectively. On this hypersurface \eqref{eq:N2}, the spectrum then organizes into multiplets of $\SU{1\vert1,1}$.
	\item {\boldmath ${\cal N}=4$} Choosing
	\begin{equation} \label{eq:N4Large}
		\begin{cases}
			\chi_{2} = \chi_{1}\,,\\% + 2\pi k\,,\\
			\ts{\chi}_{2} = -\ts{\chi}_{1}\,,% + 2\pi l / \alpha \,,
		\end{cases}
		\quad {\rm or }\quad
		\begin{cases}
			\chi_{2} = - \chi_{1}\,,\\% + 2\pi k\,,\\
			\ts{\chi}_{2} = \ts{\chi}_{1}\,,% + 2\pi l / \alpha \,,
		\end{cases}% \qquad k, l \in \mathbb{Z} \,,
	\end{equation}
	leads to enhancements to ${\cal N}=(0,4)$ and ${\cal N}=(4,0)$, respectively. On these three-dimensional hyper-surfaces \eqref{eq:N4Large}, the isometry group is $\SO{4}\times {\rm U}(1)^{2}$ and the spectrum reorganizes into multiplets of $D^{1}(2,1;\alpha)$. In the special limit where
	\begin{equation} \label{eq:limittoT4}
		\begin{cases}
			\chi_{1}=\chi_{2}= \chi,\\
			\ts{\chi}_{1}=\ts{\chi}_{2}=0,\\
			\psi=0,\\
			\alpha \rightarrow 0,
		\end{cases}
	\end{equation}
	the solution~\eqref{eq:chipsi} corresponds to the 10-dimensional uplift on $T^{4}$ of the one-parameter deformation of ${\rm AdS}_{3}\times S^{3}$ preserving ${\cal N}=(0,4)$ supersymmetries of ref.~\cite{Eloy:2021fhc} (using the notations there, the precise matching is obtained for $\chi=\sqrt{e^{2\omega}-1}$). In this limit, $D^{1}(2,1;\alpha)$ breaks into its small counterpart $\SU{2\vert1,1}$.

>>>>

Therefore, these deformations affect the Kaluza-Klein spectrum as follows: the conformal dimension of each physical field (\textit{c.f.} eq.~\eqref{eq:confdims3s3s1}) get shifted by replacing
\begin{equation} \label{eq:confdimshiftchi}
	2\pi n\longrightarrow e^{-\psi} \left[ 2\pi n + \frac{1}{2}\Big((q_{\rm L}+q_{\rm R})\,\frac{\chi_{1}}{\alpha}+(q_{\rm L}-q_{\rm R})\,\frac{\chi_{2}}{\alpha}+ (\ts{q}_{\rm L}+\ts{q}_{\rm R})\,\ts{\chi}_{1} + (\ts{q}_{\rm R}-\ts{q}_{\rm L})\,\ts{\chi}_{2}\Big) \right]\,,
\end{equation}
where the $q$ denote the charges under the different ${\rm U}(1)$.

@@

\begin{itemize}
	\item {\boldmath ${\cal N}=2$} The four-dimensional hypersurfaces
	\begin{equation} \label{eq:N2}
		\chi_{2} = \chi_{1} \pm\alpha\,(\ts{\chi}_{1}+\ts{\chi}_{2})% + 2\pi k 
		\quad {\rm or}\quad \chi_{2} = -\chi_{1} \pm\alpha\,(\ts{\chi}_{1}-\ts{\chi}_{2})% + 2\pi k \,, \qquad k \in \mathbb{Z}
		\,,
	\end{equation}
	give enhancements to ${\cal N}=(0,2)$ and ${\cal N}=(2,0)$, respectively. On this hypersurface \eqref{eq:N2}, the spectrum then organizes into multiplets of $\SU{1\vert1,1}$.
	\item {\boldmath ${\cal N}=4$} Choosing
	\begin{equation} \label{eq:N4Large}
		\begin{cases}
			\chi_{2} = \chi_{1}\,,\\% + 2\pi k\,,\\
			\ts{\chi}_{2} = -\ts{\chi}_{1}\,,% + 2\pi l / \alpha \,,
		\end{cases}
		\quad {\rm or }\quad
		\begin{cases}
			\chi_{2} = - \chi_{1}\,,\\% + 2\pi k\,,\\
			\ts{\chi}_{2} = \ts{\chi}_{1}\,,% + 2\pi l / \alpha \,,
		\end{cases}% \qquad k, l \in \mathbb{Z} \,,
	\end{equation}
	leads to enhancements to ${\cal N}=(0,4)$ and ${\cal N}=(4,0)$, respectively. On these three-dimensional hyper-surfaces \eqref{eq:N4Large}, the isometry group is $\SO{4}\times {\rm U}(1)^{2}$ and the spectrum reorganizes into multiplets of $D^{1}(2,1;\alpha)$. In the special case
	\begin{equation} \label{eq:limittoT4}
		\begin{cases}
			\chi_{1}=\chi_{2}= 0,\\
			\ts{\chi}_{1}=-\,\ts{\chi}_{2}=\sqrt{1-e^{2\omega}},\\
			\psi = -\,\omega,
		\end{cases}
	\end{equation}
	the solution~\eqref{eq:chipsi} corresponds to the 10-dimensional uplift on $S^{3}\times S^{1}$ of the one-parameter deformation of ${\rm AdS}_{3}\times S^{3}$ preserving ${\cal N}=(0,4)$ supersymmetries of ref.~\cite{Eloy:2021fhc}.
